Capstone Movielens Report

### 2025-05-12 reports/capstone-movielens-report.draft4.Rmd
Fix for report.

###### Value  {#func.tune.model_param.value}
\
The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values.

@@

###### **Details** { #func.model.tune.param_range.details } 
\

First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.

@@

The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.

@@

##### []() Function {#func.}
\

@@

##### []() Function {#func.}
\

>>>>

::: { #func.tune.model_param.value  .sidebar }
###### Value
\
The function returns a data structure containing the found value of the input parameter `param_values` for which the `RMSE` value is minimal, as well as the minimum `RMSE` value itself, along with a sequence of all calculated `RMSE` values.
:::

@@

::: { #func.model.tune.param_range.details .sidebar }
###### **Details** 
\
First, the function generates a sequence of the `input parameter values` based on the `loop_starter` parameter values, as described above (see the [loop_starter](#func.model.tune.param_range.params.loop_starter) parameter description for the details), which is used as one of the input parameters for the helper function [tune.model_param](#func.tune.model_param), which is repeatedly called during the execution, performing fine-tuning of the model.

@@

The calculation is completed when subsequent calculated values of the minimum `RMSE` stop improving and reach the most accurate possible value.
:::

@@

##### []() Function {#func.1}
\

@@

##### []() Function {#func.2}
\
